NFC and burnout in teachers - A replication and extension study

### 2021-10-26 Manuscript/Manuscript.Rmd
indentation

  fit_explor2_summ <- summary(fit_explor2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```
```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}

>>>>

  fit_explor2_summ <- summary(fit_explor2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}
